

\documentclass[letterpaper]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Tanuj Joshi}{}{ % Your name
	Address - B-13/5 Officers' Colony, Jubilant Life Sciences Ltd, Gajraula - 244233
 \\
		\href{mailto:tanuj.inn@gmail.com}{tanuj.inn@gmail.com} | +91-7351469987 % Your contact information
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Graphic Era University}
\descript{B.Tech. in Information Technology}
\location{July 2012 | July 2016} 
	     \location{ Cum. GPA: 7.7 / 10.0}

	     \sectionsep % Some whitespace after the section

	     %------------------------------------------------

	     \subsection{Birla Senior Secondary School}
	     \descript{Higher Secondary | Pilani}
	     \location{Grad. 2012 | 74.17 \%} 
         \vspace{0.5cm}
		\subsection{St. Mary's Convent School}
	     \descript{High School | Gajraula }
	     \location{Grad. 2010 | 8.8 }
   \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/in/tanuj-joshi/}
{\custombold{tanujJoshi}} \\
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\descript{Languages:}
\hspace{.5cm} \textbullet{} JAVA\\
\hspace{.5cm} \textbullet{} C\\

\descript{Oracle E-Business Suite Technologies:}
\hspace{.5cm}  \textbullet{} OAF(Oracle Application Framework) \\
\hspace{.5cm} \textbullet{} Weblogic 12c\\


\descript{Java EE Web Components APIs:}
\hspace{.5cm} \textbullet{} Java Servelets 2.3\\


\descript{Java EE Resource APIs:}

\hspace{.5cm} \textbullet{} JDBC\\
\hspace{.5cm} \textbullet{} JAX-WS\\


\descript{Application Servers:}
\hspace{.5cm} \textbullet{} Apache Tomcat\\ 
\hspace{.5cm} \textbullet{} Weblogic 12c\\

\descript{Version Control Systems:}
\hspace{.5cm} \textbullet{} GIT\\ 
\hspace{.5cm} \textbullet{} Win-CVS\\

\descript{Microsoft Technologies:}
\hspace{.5cm} \textbullet{} MS Word\\ 
\hspace{.5cm} \textbullet{} MS Excel\\
\hspace{.5cm} \textbullet{} Microsoft Visio\\

\sectionsep

\sectionsep % Some whitespace after the section

\subsection{Tools}

Eclipse \textbullet{} JDeveloper \textbullet{} Oracle E-business Suite \textbullet{} Toad for Oracle \textbullet{} SOAP-UI \textbullet{} Hadoop \textbullet{} Jira

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{WIPRO LIMITED}
\descript{Project Engineer (Core Java Developer)}
\location{28-Nov-2016 - 12-Oct-2017 | BAS-ORA-TLA-AMS-FINLAND(Telia Company)}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Monitoring and analyzing on how to control the daily inflow of service based tickets.
\item Handled Java related development to automate Manual Pro-Active task.
\item Preparing Weekly and Monthly status reports.
\item Prepared and designed the test cases for proper functioning of environments.
\end{tightemize}
\sectionsep

\runsubsection{WIPRO LIMITED}
\descript{Project Engineer (Core Java Developer)}
\location{13-Oct-2017 - Present | CSP-TEL-PJ-TELIA TNM(Telia Company)}
\begin{tightemize}
\item Responsible for OAF Page Development (Front End) and Automation of Different Channels and System to reduce manual work.
\item Handled Configurator related UI development.
\item Designing and developing JSP pages and web-services.
\item Responsible for preparing and executing manual test cases.
\item Providing support to UAT testers.
\item Design, update and review Technical Documents.
\end{tightemize}
\sectionsep

\runsubsection{Jubilant Life Sciences Ltd}
\descript{Intern}
\location{11-June-2015 to 23-July-2015 | Gajraula, UP}
\begin{tightemize}
\item Responsible for UI Development and establishing JDBC Connection.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects Undertaken}
\runsubsection{Text Passage Prediction}
\descript{| Graphic Era University}
\location{Sep, 2014 - Nov 2014 | Dehradun, Uttarakhand}
Wrote a working code to mine given text files as input and predict whether the file pertains to Amazon river or Amazon Company. The code utilized mining techniques by first parsing the text in vector form and then comparing with a sorted list of keywords.
\sectionsep

\runsubsection{Case Study for Retail Sales}
\descript{| Wipro Limited}
\location{Dec 2017 - Jan 2018 | Greater Noida, UP}
Used Scala to implement secondary sort over the given dataset. The data had to be first migrated from a SQL database to a HDFS based database (HBase). Later, the task was to secondary sort the processed data in order to optimize the queries. Significant speedup was achieved for column based queries after successful migration of data.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
Played Badminton at CBSE Zonals National Finals \\
Winner In FSLG Badminton Tournament.

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hobbies} 

Cycling \\
Playing and Watching Football/Badminton
\sectionsep


\section{Personal Details} 

Mother’s Name	:	Lalita Joshi \\
Father’s Name 	:	Harish Chandra Joshi \\
Languages Known	:	Hindi and English


\end{minipage} 
\end{document}  \documentclass[]{article}